% LaTeX resume using res.cls
\documentclass[margin]{res}
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Benjamin D. Mayes}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{6000 Reynolds Drive \#1242}
 \moveleft.5\hoffset\centerline{Rochester, NY 14623}
 \moveleft.5\hoffset\centerline{Phone (cell): (215) 595-3745}
 \moveleft.5\hoffset\centerline{Email: \tt{bdm8233@rit.edu}}
 \moveleft.5\hoffset\centerline{Github: \tt{https://github.com/Czahrien}}

\begin{resume}
 
%\section{OBJECTIVE} To further my education via a cooperative education experience in the winter or spring.
 

\section{EDUCATION} {\sl Bachelor of Science, Master of Science} Computer Science \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                Rochester Institute of Technology, Rochester, NY, 
                expected May 2013 \\
                Major: Computer Science \\
                Minors: Mathematics (in progress), Psychology (in progress) \\
                GPA: $3.97/4.00$
 
 
\section{COMPUTER \\ SKILLS} {\sl Languages:} C, C++, Haskell, Java, Standard ML, Python, Ruby, x86 assembly, MIPS assembly, Bash, \LaTeX \\
                {\sl Operating System Experience:} Linux, Mac OS X, Windows, Solaris
 
\section{PROJECT WORK}
                 {\sl Cumulonimbus:} 32-bit x86 operating system written from scratch. (C, x86 assembly) (Spring 2011)
                 \begin{itemize} \itemsep -2pt
                    \item VESA drivers and a graphics library built on top of them.
                    \item Display and input multiplexing system built on top of the process system.
                    \item Mouse and keyboard drivers.
                    \item Math library using the x87 floating point unit.
                    \item Overhauled build tree to organize the monolithic kernel and increase modularity.
                  \end{itemize}

                  {\sl archlib:} A library for CPU simulation. (C++) (Summer 2011)
                  \begin{itemize} \itemsep -2pt
                    \item Took code written for Sun's C compiler and ported it to compile under GCC 4.X.
                  \end{itemize}

                  {\sl Voting Manipulation Framework:} A framework for experimenting with various methods of election manipulation. (C++) (Summer 2010)
                  \begin{itemize} \itemsep -2pt
                    \item Implemented the concepts of a generic vote and a generic voting system.
                    \item Implemented several voting systems with the generic framework.
                    \item Provided the ability to modify an election's votes and candidates on the fly. 
                  \end{itemize}
                    
\section{EXPERIENCE} {\sl CSI Undergraduate Research Fellow} \hfill            Summer 2010 \\
                 RIT, Rochester, NY
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                    \item Read current research on computational complexity of different forms of election manipulation.
                    \item Developed a framework for simulating election manipulation.
                    \item Presented findings at the RIT Undergraduate Research Symposium.
                \end{itemize}
 
                {\sl Computer Science Theory Tutor} \hfill     Fall 2010, Winter-Spring 2012\\
                 RIT, Rochester, NY
                 \begin{itemize} \itemsep -2pt
                 \item Tutored students on topics in theoretical Computer Science.
                \end{itemize}

                {\sl Student Lab Instructor} \hfill            Fall 2011 (Python), Winter-Spring 2012 (C++) \\
                RIT, Rochester, NY
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Assisted Computer Science students with their lab work both inside and outside of the lab.
                 \item Graded submitted lab work and provided feedback. 
                \end{itemize} 
\end{resume}
\end{document}
